Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-09-20 paper/main.tex
finish With Division subsection
- add some information into appendix
  and link to it

% --------------------------------------------------------------------------------------------------
\subsection{With Division (TODO)}

@@

We can again calculate likelihood profiles for every optimized parameter.
The results displayed in Figure~\ref{fig:likelihood-profiles-comparison-with-division} show that the
values for the division lengths seem exhibit a decrease in steepness of the curve towards the left
side of the estimated parameter.
This can be attributed to the missing images which were not able to be segmented in our time series.
These results highlight a reassuring finding, namely that the method of profile-likelihood is able
to properly display this obvious lack of data.
It could be argued that this leads to a non-identifiability for the first division length while the
reamining parameters are still identifiable.
Meanwhile, the growth rates of the daughters ...

@@

%###################################################################################################
\subsection{Performance (TODO)}

@@

>>>>

% --------------------------------------------------------------------------------------------------
\subsection{With Division}

@@

We can again calculate likelihood profiles for every optimized parameter.
The results displayed in Figure~\ref{fig:likelihood-profiles-comparison-with-division} show that the
values for the division lengths exhibit a decrease in steepness of the curve towards the left side
of the estimated parameter.
This can be attributed to the missing images which were not able to be segmented in our time series.
It can be argued that this leads to a non-identifiability for the first division length while the
remaining parameters are still identifiable although the effect is also notable.
These results highlight a reassuring finding, namely that the method of profile-likelihood is able
to properly display this lack of data.
It therefore further underlines the accuracy of our methods.
In comparison, the growth rates of the daughter cells display larger variations within their
likelihood profiles.
\textbf{TODO finish this; need more results for otimization of all daughter growth rates as well}

It has to be noted that this approach is computationally much more expensive compared to the simpler
position-comparison algorithm.
There are 4 main steps which are executed within any single optimization iteration that contribute
to the total wall time.
These steps are prediction via the computational model ($15.63(21)\%$), mask adjustment of the data
masks ($14.49(19)\%$), mask rendering for the numerical results ($69.2(1.4)\%$) and finally
comparison of the masks ($0.68(5)\%$) (see section \ref{section:supplement-performance}).
The masks which are provided by the data need to be adjusted such that the identifiers of the cells
which are directly related to the chosen colors match with the ones used within the masks provided
by the data.
It is clear that the generation of masks from the numerical results takes up the majority of the
work.
In addition, the step of mask adjustment would not have been required within the position-comparison
algorithm.
Combining these two values, the position-comparison algorithm is $\approx 6.13(8)$ times faster.

@@

%###################################################################################################
\subsection{Performance (TODO)}
\label{section:supplement-performance}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/crm_divide/timings.pdf}%
    \includegraphics[width=0.5\textwidth]{figures/crm_divide/time-evolution.pdf}%
    \caption{TODO}
    \label{fig:timings-crm_divide}
\end{figure}
